\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Update some results

\begin{figure}
  \centering
  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
    \label{fig:results30}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
    \label{fig:results120}
  \end{subfigure}

@@

With an overall score of \score, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST-toolcomp22}, the score is calculated on the subset of \cuts classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. The coverage
increased from the \budgetShort to the \budgetLong search budget (mean line
coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively).

For \numTestGenFailedShort classes for \budgetShort, and \numTestGenFailedLong
classes for \budgetLong, \EVOSUITE failed to generate any tests. Unlike past
instances of the competition we found no crashes of \EVOSUITE (e.g., exceptions
thrown by \EVOSUITE) at all, but in most cases where no tests were generated
the \EVOSUITE process had been killed by the competition setup, suggesting that
\EVOSUITE was using more time than allocated. In one class of the \Seata project
errors occurred during the initialisation of the target class, in which case
\EVOSUITE simply gives up since the JVM does not allow instantiation of such
classes.

While the results for line coverage and branch coverage are similar, the
mutation scores are substantially lower. The mutation scores on the \Guava
classes are highest compared to the other three projects from which classes
were taken; this is surprising since \Guava has been known for years to be
notoriously challenging for
\EVOSUITE~\cite{campos2015continuous,almulla2017using}. However, we find that
in many cases the mutation analysis failed because dependency classes were
missing on the classpath. While \EVOSUITE, JUnit and the coverage measurement
used in the competition apparently were able to cope with this problem anyway,
the PIT mutation analysis tool was unable to deal with this problem. This may
likely be an error in the competition setup, but it would affect all test
generation tools. While \Spoon classes are affected the most, similar problems
can be observed for all projects: Considering the \budgetLong runs we found
\texttt{ClassNotFoundException}s in 414 runs for \Spoon, 309 for \Guava, 308 for
\Fastjson, and 329 for classes in \Seata; in all these cases PIT was unable to
run even when it was possible to measure coverage.

>>>>

\begin{figure}
  \centering

  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
    \label{fig:results30}
  \end{subfigure}

  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
    \label{fig:results120}
  \end{subfigure}

@@

With an overall score of \score, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST-toolcomp22}, the score is the weighted sum between the
rankings for coverage and understandability.

Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. The coverage
increased from the \budgetShort to the \budgetLong search budget (mean line
coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively).

\EVOSUITE failed to generate any tests in \numTestGenFailedShort cases with a
budget of \budgetShort, and in \numTestGenFailedLong cases with a budget of
\budgetLong. However, we found no crashes of \EVOSUITE itself (e.g., exceptions
thrown by \EVOSUITE), but in all cases where no tests were generated the
\EVOSUITE process had been killed by the competition setup, suggesting that
\EVOSUITE was using more time than allocated.

While the results for line coverage and branch coverage are similar, the
mutation scores are substantially lower. The mutation scores on the \Threeten
classes are highest compared to the other projects from which classes were taken.

For the first time, the competition also conducted a human study with 13
participants to assess test case readability. To this, a method under test
was chosen for each of the \Collections, \Threeten, and \Spatial
projects. Then, for each competitor a test covering that method was selected
randomly among the generated ones. Finally, the participants were asked
to rank the tests for each project on a scale from 1 (best) to 5 (worst),
in terms of readability. Overall, \EVOSUITE achieved the 2nd highest rank
rating. Its distribution is shown in Figure~\ref{fig:readability}.

Most participants found \EVOSUITE-generated tests to be readable. When
\EVOSUITE ranked highest, they positively highlighted the thoroughness of
generated assertions, using edge cases as inputs, and the fact that tests
where short. When \EVOSUITE ranked lowest, participants criticised the lack
of comments and descriptive test names, repetitiveness in the code, and
needless assertions.

Among the tests for \Collections the longest one was produced by \EVOSUITE.
Interestingly, it ranked both highest and lowest, with one participant
stating it was ``the most complete'', while another suggested the code
being longer makes it ``more confusing''.

\begin{figure}
  \includegraphics[width=0.9\columnwidth]{./data/understandability}
  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project.}
  \label{fig:readability}
\end{figure}
